Dancing on Water: The Choreography of Sulfur Dioxide Adsorption to Aqueous Surfaces

### 2011-07-01 Methods.tex
Starting draft 9

This method for finding the outer monolayer location was implemented, and the surface location is plotted as a function of simulation time in Figure \ref{fig:density-flaw}B. It is apparent from the surface location plot that the water slab location, and thus the surface location, drifts over the 10 ns, spanning approx. 12 $\AA$. However, the maximum standard deviation of the positions of the waters comprising the surface layer at each time step is only 1.85 $\AA$. Consequently, all depth locations in our analyses are calculated relative to the instantaneous surface location at the corresponding time step of the trajectories.

>>>>

This method for finding the outer monolayer location was implemented, and the surface location is plotted as a function of simulation time in Figure \ref{fig:density-flaw}B. It is apparent from the surface location plot that the water slab location, and thus the surface location, drifts over the 10 ns, spanning approximately 12 $\AA$. However, the maximum standard deviation of the positions of the waters comprising the surface layer at each time step is only 1.85 $\AA$. Consequently, all depth locations in our analyses are calculated relative to the instantaneous surface location at the corresponding time step of the trajectories.
